Stability and accuracy of free surface time integration in viscous flows

### 2016-11-02 free-surface-paper.tex
Add pseudocode description.

\subsection{Choice of $\tau^*$}
As discussed above, a full geodynamic simulation will have a spectrum of relaxation times.
For complete stability, the parameter $\tau^*$ should be chosen such that every mode is stable.
In practice, this means that a good choice is 
\begin{equation}
\tau^* \approx \tau_{\mathrm{min}}.
\label{eq:tau_choice}
\end{equation}

@@

\begin{equation}
\int_{\Gamma_F} \mathbf{w} \cdot \mathbf{u}_\mathrm{mesh} = 
\int_{\Gamma_F} \left( \mathbf{w \cdot n } \right) \left( \mathbf{u \cdot n} \right).
\end{equation}
When discretized, this forms a linear system which can be solved for the mesh velocity $\mathbf{u}_\mathrm{mesh}$ at the 
free surface. A new system to solve is not ideal, but this system, being nonzero 
over only the free surface, is relatively computationally inexpensive to solve.

@@

>>>>

\subsection{Choice of $\tau^*$}
\label{sec:tau_choice}
As discussed above, a full geodynamic simulation will have a spectrum of relaxation times.
For complete stability, the parameter $\tau^*$ should be chosen such that every mode is stable.
In practice, this means that a good choice is 
\begin{equation}
\tau^* \approx \tau_{\mathrm{min}}.
\label{eq:tau_choice}
\end{equation}

@@

\begin{equation}
\int_{\Gamma_F} \mathbf{w} \cdot \mathbf{u}_\mathrm{mesh} = 
\int_{\Gamma_F} \left( \mathbf{w \cdot n } \right) \left( \mathbf{u \cdot n} \right).
  \label{eq:mesh_velocity_system}
\end{equation}
When discretized, this forms a linear system which can be solved for the mesh velocity $\mathbf{u}_\mathrm{mesh}$ at the 
free surface. A new system to solve is not ideal, but this system, being nonzero 
over only the free surface, is relatively computationally inexpensive to solve.

@@

\subsection{Summary of the implementation}
We summarize this section by describing pseudocode for the implementation.
There are two variations, one using the quasi-implicit scheme and one using nonstandard finite differences.

For the quasi-implicit scheme:
\begin{enumerate}
  \item Solve the Stokes system, including the boundary term given in Equation~\eqref{eq:kmm}, 
    which is a function of timestep $t^n$ and $\theta$.
  \item Solve for the surface mesh velocity using Equation~\eqref{eq:mesh_velocity_system}.
  \item Solve for the internal mesh velocity using Equations~\eqref{eq:laplacian_smoothing}~-~\eqref{eq:laplacian_bcs}.
  \item Advect the mesh forward in time using displacements determined by the forward Euler scheme: $\mathbf{x}(t^{n+1}) = \mathbf{x}(t^n) + \mathbf{u}_\mathrm{mesh}\Delta t$.
\end{enumerate}

For the nonstandard finite difference scheme:
\begin{enumerate}
  \item Estimate $\tau_\mathrm{min}$ using one of the means described in Section~\ref{sec:tau_choice}.
  \item Solve the Stokes system normally.
  \item Solve for the surface mesh velocity using Equation~\eqref{eq:mesh_velocity_system}.
  \item Solve for the internal mesh velocity using Equations~\eqref{eq:laplacian_smoothing}~-~\eqref{eq:laplacian_bcs}.
  \item Advect the mesh forward in time using displacements determined by the nonstandard finite difference scheme (Equation~\eqref{eq:nsfd}).
\end{enumerate}
